---
title: "The Importance of Normality Assumption in Large Public Health Data Sets"
output: html_notebook
---

Data Exploration
```{r include=FALSE}
library(moments)
library(tidyverse)
library(lmtest)
library(car)
```
```{r}
data <- read.table("~/Desktop/SASUniversityEdition/FL_insurance_sample 2.csv", header=TRUE, sep=",")
head(data)
dim(data)
hist(data$tiv_2012, xlim=c(0, 1.5e+07), breaks=1000)
skewness(data$tiv_2012)
kurtosis(data$tiv_2012)
summary(data$tiv_2012)
```
Example of Central Limit Theorem:

Sampling distribution of 1000 means of random samples of size 1%, 2%, 5%, 7.5%, 10%, 15%, and 20% of the population from this very non-Normal distribution. 
```{r}
sampler <- function(dat, pct) {
  ans_vec <- rep(0,times=1000)
  for(i in 1:1000) {
    ans_ <- sample(dat, size=pct*36634)
    ans_vec[i] <- mean(ans_)
  }
  return(ans_vec)
}

set.seed(1234567890)

par(mfrow=c(2,3))

# s_1 <- sampler(dat=data$tiv_2012, pct=0.01)
# skewness(s_1)
# hist(s_1, xlim=c(7e+05,6.5e+06), main="1%", xlab="Dollars", breaks=44, freq=FALSE)
# x <- seq(7e+05,6.5e+06)
# curve(dnorm(x, mean=mean(s_1), sd=sd(s_1)), add=TRUE)
# abline(v=mean(s_1), col="red", lty=1, lwd=2)

s_2 <- sampler(dat=data$tiv_2012,pct=0.02)
skewness(s_2)
hist(s_2, xlim=c(7e+05,6.5e+06), main="2%", xlab="Dollars",breaks=44, freq=FALSE)
curve(dnorm(x, mean=mean(s_2), sd=sd(s_2)), add=TRUE)
abline(v=mean(s_2), col="red", lty=1, lwd=2)

s_5 <- sampler(dat=data$tiv_2012, pct=0.05)
skewness(s_5)
hist(s_5, xlim=c(7e+05,6.5e+06), main="5%", xlab="Dollars", breaks=11, freq=FALSE)
curve(dnorm(x, mean=mean(s_5), sd=sd(s_5)), add=TRUE)
abline(v=mean(s_5), col="red", lty=1, lwd=2)

s_7_5 <- sampler(dat=data$tiv_2012, pct=0.075)
skewness(s_7_5)
hist(s_7_5, xlim=c(7e+05,6.5e+06), main="7.5%", xlab="Dollars", breaks=11, freq=FALSE)
curve(dnorm(x, mean=mean(s_7_5), sd=sd(s_7_5)), add=TRUE)
abline(v=mean(s_7_5), col="red", lty=1, lwd=2)

s_10 <- sampler(dat=data$tiv_2012, pct=0.1)
skewness(s_10)
hist(s_10, xlim=c(7e+05,6.5e+06), main="10%", xlab="Dollars", breaks=11, freq=FALSE)
curve(dnorm(x, mean=mean(s_10), sd=sd(s_10)), add=TRUE)
abline(v=mean(s_10), col="red", lty=1, lwd=2)

s_15 <- sampler(dat=data$tiv_2012, pct=0.15)
skewness(s_15)
hist(s_15, xlim=c(7e+05,6.5e+06), main="15%", xlab="Dollars", breaks=11, freq=FALSE)
curve(dnorm(x, mean=mean(s_15), sd=sd(s_15)), add=TRUE)
abline(v=mean(s_15), col="red", lty=1, lwd=2)

s_20 <- sampler(dat=data$tiv_2012, pct=0.20)
skewness(s_20)
hist(s_20, xlim=c(7e+05,6.5e+06), main="20%", xlab="Dollars", breaks=11, freq=FALSE)
curve(dnorm(x, mean=mean(s_20), sd=sd(s_20)), add=TRUE)
abline(v=mean(s_20), col="red", lty=1, lwd=2)

```
We drew 1000 1% samples, of average size 65, from the population. For each sample we calculated the regression of cost on age, sex, self-rated health, and HMO (IPA = 0) versus Fee for Service (IPA = 1). % of population, N in sample, Mean
```{r}
coeff_cmp <- function(pop_coeff, smp_confint) {
  
  tiv12 <- pop_coeff[2]; rc <- pop_coeff[3]; rm <- pop_coeff[4]; sf <- pop_coeff[5]; #wd <- pop_coeff[6]
  pct_tiv12 <- rep(0,1000); pct_rc <- rep(0,1000); pct_rm <- rep(0,1000); pct_sf <- rep(0,1000); #pct_wd <- rep(0,1000)
  
  for(i in 1:1000) {
    s_tiv12 <- c(smp_confint[[i]][2,1], smp_confint[[i]][2,2])
    s_rc <- c(smp_confint[[i]][3,1], smp_confint[[i]][3,2])
    s_rm <- c(smp_confint[[i]][4,1], smp_confint[[i]][4,2])
    s_sf <- c(smp_confint[[i]][5,1], smp_confint[[i]][5,2])
    #s_wd <- c(smp_confint[[i]][6,1], smp_confint[[i]][6,2])
    
    pct_tiv12[i] <- s_tiv12[1] <= tiv12 && tiv12 <= s_tiv12[2]
    pct_rc[i] <- s_rc[1] <= rc && rc <= s_rc[2]
    pct_rm[i] <- s_rm[1] <= rm && rm <= s_rm[2]
    pct_sf[i] <- s_sf[1] <= sf && sf <= s_sf[2]
    #pct_wd[i] <- s_wd[1] <= wd && wd <= s_wd[2]
    
  }
  
  pct1_tiv12 <- (sum(pct_tiv12==TRUE)/1000)*100
  pct1_rc <- (sum(pct_rc==TRUE)/1000)*100
  pct1_rm <- (sum(pct_rm==TRUE)/1000)*100
  pct1_sf <- (sum(pct_sf==TRUE)/1000)*100
  #pct1_wd <- sum(pct_wd==TRUE)/1000
  
  ans_vec <- c(pct1_tiv12, pct1_rc, pct1_rm, pct1_sf)
  
  return(ans_vec)
}
```
```{r}
sampler_lg <- function(dat, pct) {
  ans_mat <- list()
  
  for(i in 1:1000) {
    ans_mat[[i]] <- sample_n(dat, size=pct*36634)
  }
  return(ans_mat)
}
```
```{r}

fit <- lm(tiv_2011 ~ tiv_2012*construction, data=data)
fit_coeff <- confint(fit)
par(mfrow=c(2,2))
plot(fit)

lmtest::bptest(fit) # Breusch-Pagan test for heteroscedascity
car::ncvTest(fit)

set.seed(1234567890)

new_data <- data[c("tiv_2011", "tiv_2012", "construction")]


# 1%
s_1_ <- sampler_lg(dat=new_data, pct=0.01)

s_1_fit <- list()
s_1_fit_coeffs <- list()
s_1_fit_confint <- list()

for(i in 1:1000) {
   s_1_fit[[i]] <- lm(s_1_[[i]]$tiv_2011 ~ s_1_[[i]]$tiv_2012 + s_1_[[i]]$construction, data=s_1_[[i]])
   s_1_fit_confint[[i]] <- confint(s_1_fit[[i]], level=0.95)
   s_1_fit_coeffs[[i]] <- s_1_fit[[i]]$coefficients
}
coeff_cmp(pop_coeff=fit_coeff, smp_confint=s_1_fit_confint)


# 2%
s_2_ <- sampler_lg(dat=new_data, pct=0.02)

s_2_fit <- list()
s_2_fit_coeffs <- list()
s_2_fit_confint <- list()

for(i in 1:1000) {
   s_2_fit[[i]] <- lm(s_2_[[i]]$tiv_2011 ~ s_2_[[i]]$tiv_2012 + s_2_[[i]]$construction, data=s_2_[[i]])
   s_2_fit_confint[[i]] <- confint(s_2_fit[[i]], level=0.95)
   s_2_fit_coeffs[[i]] <- s_2_fit[[i]]$coefficients
}
coeff_cmp(pop_coeff=fit_coeff, smp_confint=s_2_fit_confint)

# 5%
s_5_ <- sampler_lg(dat=new_data, pct=0.05)

s_5_fit <- list()
s_5_fit_coeffs <- list()
s_5_fit_confint <- list()

for(i in 1:1000) {
   s_5_fit[[i]] <- lm(s_5_[[i]]$tiv_2011 ~ s_5_[[i]]$tiv_2012 + s_5_[[i]]$construction, data=s_5_[[i]])
   s_5_fit_confint[[i]] <- confint(s_5_fit[[i]], level=0.95)
   s_5_fit_coeffs[[i]] <- s_5_fit[[i]]$coefficients
}
coeff_cmp(pop_coeff=fit_coeff, smp_confint=s_5_fit_confint)

# 7.5%
s_75_ <- sampler_lg(dat=new_data, pct=0.075)

s_75_fit <- list()
s_75_fit_coeffs <- list()
s_75_fit_confint <- list()

for(i in 1:1000) {
   s_75_fit[[i]] <- lm(s_75_[[i]]$tiv_2011 ~ s_75_[[i]]$tiv_2012 + s_75_[[i]]$construction, data=s_75_[[i]])
   s_75_fit_confint[[i]] <- confint(s_75_fit[[i]], level=0.95)
   s_75_fit_coeffs[[i]] <- s_75_fit[[i]]$coefficients
}
coeff_cmp(pop_coeff=fit_coeff, smp_confint=s_75_fit_confint)

# 10%
s_10_ <- sampler_lg(dat=new_data, pct=0.1)

s_10_fit <- list()
s_10_fit_coeffs <- list()
s_10_fit_confint <- list()

for(i in 1:1000) {
   s_10_fit[[i]] <- lm(s_10_[[i]]$tiv_2011 ~ s_10_[[i]]$tiv_2012 + s_10_[[i]]$construction, data=s_1_[[i]])
   s_10_fit_confint[[i]] <- confint(s_1_fit[[i]], level=0.95)
   s_10_fit_coeffs[[i]] <- s_10_fit[[i]]$coefficients
}
coeff_cmp(pop_coeff=fit_coeff, smp_confint=s_10_fit_confint)

# 15%
s_15_ <- sampler_lg(dat=new_data, pct=0.15)

s_15_fit <- list()
s_15_fit_coeffs <- list()
s_15_fit_confint <- list()

for(i in 1:1000) {
   s_15_fit[[i]] <- lm(s_15_[[i]]$tiv_2011 ~ s_15_[[i]]$tiv_2012 + s_15_[[i]]$construction, data=s_15_[[i]])
   s_15_fit_confint[[i]] <- confint(s_15_fit[[i]], level=0.95)
   s_15_fit_coeffs[[i]] <- s_15_fit[[i]]$coefficients
}
coeff_cmp(pop_coeff=fit_coeff, smp_confint=s_15_fit_confint)


# 20%
s_20_ <- sampler_lg(dat=new_data, pct=0.2)

s_20_fit <- list()
s_20_fit_coeffs <- list()
s_20_fit_confint <- list()

for(i in 1:1000) {
   s_20_fit[[i]] <- lm(s_20_[[i]]$tiv_2011 ~ s_20_[[i]]$tiv_2012 + s_20_[[i]]$construction, data=s_20_[[i]])
   s_20_fit_confint[[i]] <- confint(s_20_fit[[i]], level=0.95)
   s_20_fit_coeffs[[i]] <- s_20_fit[[i]]$coefficients
 }
coeff_cmp(pop_coeff=fit_coeff, smp_confint=s_20_fit_confint)

```